The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-10 paper/ms.tex
Update orbits table, other small edits

\begin{deluxetable*}{cccccccc}
\tablecaption{Description and names of the three orbits considered in this
work. For the last two columns: $z_{\text{max}}$ is the maximum height of the
orbit while $\frac{1}{2}(R_{\text{max}} - R_{\text{min}})$ is the magnitude of
the radial excursions of the orbit. In the epicyclic approximation, $A_z =
z_{\text{max}}$ and $A_R = \frac{1}{2}(R_{\text{max}} - R_{\text{min}})$.
\label{tab:orbits}}
\tablehead{\colhead{name} & \colhead{initial position} & \colhead{initial
velocity} & \colhead{$J_R$} &
\colhead{$J_{\phi}$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} &
\colhead{$\frac{1}{2}(R_{\text{max}} - R_{\text{min}})$}\\ \colhead{ } &
\colhead{$\mathrm{kpc}$} & \colhead{$\mathrm{km}/\mathrm{s}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc}$} & \colhead{$\mathrm{kpc}$}}
\startdata 
thin-disk & $(8, 0, 0)$ & $(0, -190, 10)$ & 40.3 & -1520 & 0.69 & 0.12 & 1.29 \\
thick-disk & $(8, 0, 0)$ & $(0, -190, 50)$ & 32.5 & -1520 & 23.0 & 0.85 & 1.19 \\ 
halo & $(8, 0, 0)$ & $(0, -190, 190)$ & 32.8 & -1520 & 529.1 & 6.16 & 2.34
\enddata
\end{deluxetable*}

@@

In Figure~\ref{fig:Jphi_JR_hist} we plot the distribution of $J_R$ as a
function of orbital phase induced by an offset in $x$ and $z$ and the
distribution of $J_{\phi}$ for an offset in $x$. We plot the distributions for
the thick-disk (upper panels) and thin-disk (lower panels) orbits.

We find that the $J_R$ distribution induced by an offset in $x$ more
closely resembles a Gaussian, while the $J_R$ distribution induced by
an offset in $z$ and the $J_{\phi}$ distribution induced by an offset
in $x$ are both similar to the $J_z$ distribution induced by an
offset in $z$ (see Figure~\ref{fig:Jz_hist}).

>>>>

\begin{deluxetable*}{cCCCCCCCCC}
\tablecaption{Description and names of the three orbits considered in this
work. For the last four columns: $z_{\text{max}}$ is the maximum height of the
orbit, $\frac{1}{2}(R_{\text{max}} - R_{\text{min}})$ is the magnitude of
the radial excursions of the orbit, and $\kappa$ and $\nu$ are the radial/epicyclic and vertical frequencies of the orbit. In the epicyclic approximation, $A_z =
z_{\text{max}}$ and $A_R = \frac{1}{2}(R_{\text{max}} - R_{\text{min}})$.
\label{tab:orbits}}
\tablehead{\colhead{name} & \colhead{initial position} & \colhead{initial
velocity} & \colhead{$J_R$} &
\colhead{$J_{\phi}$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} &
\colhead{$\frac{1}{2}(R_{\text{max}} - R_{\text{min}})$} & \colhead{$\kappa$} & \colhead{$\nu$} \\ \colhead{ } &
\colhead{$\mathrm{kpc}$} & \colhead{$\mathrm{km\,s}^{-1}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc}$} & \colhead{$\mathrm{kpc}$} & \colhead{$\mathrm{Myr}^{-1}$} & \colhead{$\mathrm{Myr}^{-1}$}}
\startdata 
thin-disk & (8, 0, 0) & (0, -190, 10) & 40.3 & -1520 & 0.69 & 0.12 & 1.29 & 0.049 & 0.093 \\
thick-disk & (8, 0, 0) & (0, -190, 50) & 32.5 & -1520 & 23.0 & 0.85 & 1.19 & 0.048 & 0.061 \\ 
halo & (8, 0, 0) & (0, -190, 190) & 32.8 & -1520 & 529.1 & 6.16 & 2.34 & 0.033 & 0.025
\enddata
\end{deluxetable*}

@@

In Figure~\ref{fig:Jphi_JR_hist} we plot the distribution of $J_R$ as a
function of orbital phase induced by an offset in $x$ and $z$ and the
distribution of $J_{\phi}$ for an offset in $x$. We plot the distributions for
the thick-disk (upper panels) and thin-disk (lower panels) orbits. We find that the $J_R$ distribution induced by an offset in $x$ more
closely resembles a Gaussian, while the $J_R$ distribution induced by
an offset in $z$ and the $J_{\phi}$ distribution induced by an offset
in $x$ are both similar to the $J_z$ distribution induced by an
offset in $z$ (see Figure~\ref{fig:Jz_hist}).
